---
title: "Category Learning Data Processing"
author: "Kayleigh Ryherd"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

Read in data, load libraries, set working directory.
```{r}
library(Rmisc)
library(tidyverse)
setwd("~/dissertation/DataAnalysis/Exp2/CatLearning")
ashby <- read.csv("Ashby_concat_11-13-18_1221.csv")
sloutsky <- read.csv("Sloutsky_concat_11-13-18_1150.csv")
taxthem <- read.csv("taxthem_concat_11-13-18_1356.csv")
```

# Processing/Standardizing Ashby Data

```{r}
# check block names
levels(as.factor(ashby$Block))
# edit typo
ashby$Block[ashby$Block == 33] <- 3
# create across-block trial value
ashby$Overall_Trial <- (ashby$Block-1)*80 + ashby$Trial
# select only blocks 1 - 3
ashby_filt <- filter(ashby, Block <= 3)
```

Check to see which subjects have missing blocks.

```{r}
missings <- ashby_filt %>% 
  group_by(Subject, Type) %>% 
  summarise(count = n()) %>% 
  filter(count < 240)
```

Look at data by condition.

```{r}
acc <- ashby_filt %>%
  group_by(Subject, Type) %>%
  summarise(m_acc = mean(Accuracy))

acc_wide <- spread(acc, Type, m_acc)
ggplot(acc_wide, aes(RB, II)) + geom_point() + theme_bw() + geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Ashby Conditions")

acc_plot <- summarySE(acc, "m_acc", "Type")
ggplot(acc, aes(Type, m_acc)) + geom_violin() + 
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = acc_plot) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = acc_plot) +
  theme_bw() + xlab("Condition") + ylab("Accuracy") + ggtitle("Ashby Performance")
```

Look at data by block and condition.

```{r}
acc_block <- ashby_filt %>%
  group_by(Subject, Type, Block) %>%
  summarise(m_acc = mean(Accuracy))
acc_block$Block <- as.factor(acc_block$Block)

acc_plot <- summarySE(acc_block, "m_acc", c("Type", "Block"))
ggplot(acc_block, aes(Block, m_acc)) + geom_violin() +
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = acc_plot) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = acc_plot) +
  facet_grid(.~Type) +
  theme_bw() + xlab("Block") + ylab("Accuracy") + ggtitle("Ashby Performance by Block")
```

Create *z*-scores for accuracy.

```{r}
acc$acc_z <- scale(acc$m_acc)
acc$System <- NA
acc$System[acc$Type == "II"] <- "associative"
acc$System[acc$Type == "RB"] <- "hypothesis-testing"
```

# Processing/Standardizing Sloutsky Data

Accuracy -- accuracy is all pretty high.
```{r}
sl_acc <- sloutsky %>%
  group_by(Subject, Block) %>%
  summarise(m_acc = mean(Accuracy))

sl_plot_acc <- summarySE(sl_acc, "m_acc", "Block")
ggplot(sl_acc, aes(Block, m_acc)) + geom_violin() + 
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = sl_plot_acc) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = sl_plot_acc) +
  theme_bw() + xlab("Block") + ylab("Accuracy") + ggtitle("Sloutsky Performance")
```

Reaction time

```{r}
sloutsky$RT[sloutsky$RT == 9999] <- NA
sl_rt <- sloutsky %>%
  filter(Accuracy == 1 & RT > 0.250) %>%
  group_by(Subject, Block) %>%
  summarise(m_RT = mean(RT, na.rm = TRUE))

sl_plot_rt <- summarySE(sl_rt, "m_RT", "Block", na.rm = TRUE)
ggplot(sl_rt, aes(Block, m_RT)) + geom_violin() + 
  geom_point(aes(y = m_RT), size = 2, position = position_dodge((width = 0.90)), data = sl_plot_rt) +
  geom_errorbar(aes(ymin = m_RT-se, ymax = m_RT+se), width = 0.20, position = position_dodge((width = 0.90)), data = sl_plot_rt) +
  theme_bw() + xlab("Block") + ylab("RT") + ggtitle("Sloutsky Performance")
```

Comparing SS to UD. It doesn't look like ACC is helpful here.

```{r}
sl_filt <- filter(sl_acc, Block %in% c("SupervisedSparse","UnsupervisedDense"))
sl_wide <- spread(sl_filt, Block, m_acc)
ggplot(sl_wide, aes(UnsupervisedDense, SupervisedSparse)) + geom_point() + theme_bw() + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Sloutsky Conditions - ACC")

sl_filt <- filter(sl_rt, Block %in% c("SupervisedSparse","UnsupervisedDense"))
sl_wide <- spread(sl_filt, Block, m_RT)
ggplot(sl_wide, aes(UnsupervisedDense, SupervisedSparse)) + geom_point() + theme_bw() + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Sloutsky Conditions - RT")
```

Standardizing Sloutsky RTs.

```{r}
sl_filt$rt_z <- scale(sl_filt$m_RT)
sl_filt$System <- NA
sl_filt$System[sl_filt$Block == "UnsupervisedDense"] <- "associative"
sl_filt$System[sl_filt$Block == "SupervisedSparse"] <- "hypothesis-testing"
```

# Processing/Standardizing Tax/Them Data

Accuracy

```{r}
test_trials <- filter(taxthem, !is.na(expTrials.thisTrialN))

tt_acc <- test_trials %>%
  group_by(participant, Experiment) %>%
  summarise(m_acc = mean(resp.corr))

tt_plot_acc <- summarySE(tt_acc, "m_acc", "Experiment")
ggplot(tt_acc, aes(Experiment, m_acc)) + geom_violin() + 
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = tt_plot_acc) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = tt_plot_acc) +
  theme_bw() + xlab("Condition") + ylab("Accuracy") + ggtitle("Tax/Them Performance")
```

RT

```{r}
# remove RTs that are too short (less than 250ms), incorrect trials
cor_trials <- filter(test_trials, resp.corr == 1 & resp.rt > 0.250)

tt_rt <- cor_trials %>%
  group_by(participant, Experiment) %>%
  summarise(m_RT = mean(resp.rt))

tt_plot_rt <- summarySE(tt_rt, "m_RT", "Experiment")
ggplot(tt_rt, aes(Experiment, m_RT)) + geom_violin() + 
  geom_point(aes(y = m_RT), size = 2, position = position_dodge((width = 0.90)), data = tt_plot_rt) +
  geom_errorbar(aes(ymin = m_RT-se, ymax = m_RT+se), width = 0.20, position = position_dodge((width = 0.90)), data = tt_plot_rt) +
  theme_bw() + xlab("Condition") + ylab("RT") + ggtitle("Tax/Them Performance")

tt_wide <- spread(tt_rt, Experiment, m_RT)
ggplot(tt_wide, aes(taxonomic, thematic)) + geom_point() + theme_bw() + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between TaxThem Conditions - RT")

tt_rt$rt_z <- scale(tt_rt$m_RT)
tt_rt$System <- NA
tt_rt$System[tt_rt$Experiment == "taxonomic"] <- "associative"
tt_rt$System[tt_rt$Experiment == "thematic"] <- "hypothesis-testing"
```
