---
title: "Category Learning Data Processing"
author: "Kayleigh Ryherd"
date: "11/13/2018"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

Read in data, load libraries, set working directory.

```{r load_data}
library(Rmisc)
library(tidyverse)
library(neuropsychology)
library(lme4)
library(lmerTest)
library(fBasics)
library(caret)
library(multcomp)
library(ggcorrplot)
library(multcomp)
setwd("~/dissertation/DataAnalysis/Exp2/CatLearning")
ashby <- read.csv("Ashby_concat_12-07-18_1019.csv")
sloutsky <- read.csv("Sloutsky_concat_02-14-19_1352.csv")
taxthem <- read.csv("taxthem_concat_12-07-18_1020.csv")
age_gender <- read.csv("../age_gender.csv")
'%!in%' <- function(x,y)!('%in%'(x,y))
```

# Processing/Standardizing Ashby Data

```{r}
# check block names
levels(as.factor(ashby$Block))
# edit typo
ashby$Block[ashby$Block == 33] <- 3
# create across-block trial value
ashby$Overall_Trial <- (ashby$Block-1)*80 + ashby$Trial
# select only blocks 1 - 3
ashby_filt <- dplyr::filter(ashby, Block <= 3)
```

Check to see which subjects have missing blocks & remove those subjects. This means any subject with less than 240 trials (3 full blocks) is dropped.

```{r}
complete <- ashby_filt %>% 
  group_by(Subject, Type) %>% 
  summarise(count = n()) %>% 
  dplyr::filter(count == 240) %>%
  spread(key = Type, value = count) %>%
  na.omit
nrow(complete)
complete_ashby_blocks <- complete$Subject
ashby_full <- ashby_filt %>%
  dplyr::filter(Subject %in% complete_ashby_blocks)
```

## Accuracy


```{r}
# mean accuracy by subject and system
ashby_acc_long <- ashby_full %>%
  group_by(Subject, Type) %>%
  dplyr::filter(Block == 3) %>%
  summarise(m_acc = mean(Accuracy))

# plot relationship between systems
ashby_acc_wide <- spread(ashby_acc_long, Type, m_acc)
ggplot(ashby_acc_wide, aes(RB, II)) + geom_point() + theme_bw() + geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Ashby Systems - Accuracy")

# test correlation
cor.test(ashby_acc_wide$RB, ashby_acc_wide$II)

# violin plot by system
ashby_acc_plot <- summarySE(ashby_acc_long, "m_acc", "Type")
ggplot(ashby_acc_long, aes(Type, m_acc)) + geom_violin() + 
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = ashby_acc_plot) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = ashby_acc_plot) +
  theme_bw() + xlab("Condition") + ylab("Accuracy") + ggtitle("Ashby Performance")

# summarize by block, system, and subject
ashby_acc_block <- ashby_full %>%
  group_by(Subject, Type, Block) %>%
  summarise(m_acc = mean(Accuracy))
ashby_acc_block$Block <- as.factor(ashby_acc_block$Block)

# plot by system and block
ashby_acc_plot <- summarySE(ashby_acc_block, "m_acc", c("Type", "Block"))
ggplot(ashby_acc_block, aes(Block, m_acc)) + geom_violin() +
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = ashby_acc_plot) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = ashby_acc_plot) +
  facet_grid(.~Type) +
  theme_bw() + xlab("Block") + ylab("Accuracy") + ggtitle("Ashby Performance by Block")
```

Create *z*-scores for accuracy.

```{r}
# select new data frame
ashby_acc_stand <- ashby_acc_long
# z-scores
ashby_acc_stand$acc_z <- scale(ashby_acc_stand$m_acc)
# create column for system
ashby_acc_stand$System <- NA
ashby_acc_stand$System[ashby_acc_stand$Type == "II"] <- "associative"
ashby_acc_stand$System[ashby_acc_stand$Type == "RB"] <- "hypothesis-testing"
# create column for paradigm
ashby_acc_stand$CatLearn <- "ashby"
# create df with raw ACC values
ashby_acc <- ashby_acc_stand[,-c(2,4)]
# create df with ACC z-scores
ashby_acc_stand <- ashby_acc_stand[,-c(2,3)]
```

## RT

RT Filtering (Lachaud & Renaud, 2011)

- ideal: +/- 2SD by item and by subject
- can't do by item, but we can do by subject nd type (RB vs II).

```{r}
# filter RTs and then calculate mean RT by subject
ashby_rt_long <- ashby_full %>%
  dplyr::filter(Accuracy == 1) %>% # selecting correct trials only
  group_by(Subject, Type) %>%
  mutate(mean_rt = mean(RT),
         sd_rt = sd(RT),
         diff = RT-mean_rt,
         remove = ifelse(abs(diff) > 2*sd_rt, 1, 0)) %>% # if any trial has an RT more than 2SD away from the mean, flag it for removal
  dplyr::filter(remove == 0, Block == 3) %>% # remove those trials, choose only block 3
  summarise(m_rt = mean(RT))

ashby_rt_wide <- spread(ashby_rt_long, Type, m_rt)
ggplot(ashby_rt_wide, aes(RB, II)) + geom_point() + theme_bw() + geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Ashby Conditions - RT")

# check for subjects who are total outliers within a given system

is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}
ashby_rt_long %>%
  group_by(Type) %>%
  mutate(outlier = ifelse(is_outlier(m_rt), Subject, as.numeric(NA))) %>%
  ggplot(., aes(Type, m_rt)) + geom_boxplot() + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3) + theme_bw()
```

One subject has weirdly long RTs for both systems. I'm going to remove them from the analysis.

```{r}
ashby_rt_long <- ashby_rt_long %>%
  dplyr::filter(Subject != 8088)

ashby_rt_wide <- ashby_rt_wide %>%
  dplyr::filter(Subject != 8088)

# plot relationship between two systems
ggplot(ashby_rt_wide, aes(RB, II)) + geom_point() + theme_bw() + geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Ashby Systems - RT")

# test correlation
cor.test(ashby_rt_wide$RB, ashby_rt_wide$II)

# violin plot of RTs by system
ashby_rt_plot <- summarySE(ashby_rt_long, "m_rt", "Type")
ggplot(ashby_rt_long, aes(Type, m_rt)) + geom_violin() + 
  geom_point(aes(y = m_rt), size = 2, position = position_dodge((width = 0.90)), data = ashby_rt_plot) +
  geom_errorbar(aes(ymin = m_rt-se, ymax = m_rt+se), width = 0.20, position = position_dodge((width = 0.90)), data = ashby_rt_plot) +
  theme_bw() + xlab("Condition") + ylab("RT") + ggtitle("Ashby Performance")

# summarise by subject, system, and block
ashby_rt_block <- ashby_full %>%
  dplyr::filter(Accuracy == 1, Subject != 8088) %>% # selecting correct trials only, removing outlier subject
  group_by(Subject, Type, Block) %>%
  mutate(mean_rt = mean(RT),
         sd_rt = sd(RT),
         diff = RT-mean_rt,
         remove = ifelse(abs(diff) > 2*sd_rt, 1, 0)) %>%
  dplyr::filter(remove == 0) %>%
  summarise(m_rt = mean(RT))
ashby_rt_block$Block <- as.factor(ashby_rt_block$Block)

# plot by block and system
ashby_rt_plot <- summarySE(ashby_rt_block, "m_rt", c("Type", "Block"))
ggplot(ashby_rt_block, aes(Block, m_rt)) + geom_violin() +
  geom_point(aes(y = m_rt), size = 2, position = position_dodge((width = 0.90)), data = ashby_rt_plot) +
  geom_errorbar(aes(ymin = m_rt-se, ymax = m_rt+se), width = 0.20, position = position_dodge((width = 0.90)), data = ashby_rt_plot) +
  facet_grid(.~Type) +
  theme_bw() + xlab("Block") + ylab("RT") + ggtitle("Ashby Performance by Block")
```

Create *z*-scores for accuracy.

```{r}
# select new df
ashby_rt_stand <- ashby_rt_long
# create z-scores
ashby_rt_stand$rt_z <- scale(ashby_rt_stand$m_rt)
# create column for system
ashby_rt_stand$System <- NA
ashby_rt_stand$System[ashby_rt_stand$Type == "II"] <- "associative"
ashby_rt_stand$System[ashby_rt_stand$Type == "RB"] <- "hypothesis-testing"
# create column for paradigm
ashby_rt_stand$CatLearn <- "ashby"
# df with raw RTs
ashby_rt <- ashby_rt_stand[,-c(2,4)]
# df with RT z-scores
ashby_rt_stand <- ashby_rt_stand[,-c(2:3)]
```


# Processing/Standardizing Sloutsky Data

## Accuracy

I have used d' in the past, but I want this to be totally relatable between tasks. I'm going to calculate regular accuracy here.

```{r}
# remove subjects with less than 6 correct on the catch trials
poor_blocks <- sloutsky %>%
  dplyr::filter(substr(Stimulus,1,5) =="catch") %>%
  group_by(Subject,Block) %>%
  summarise(catch_acc = mean(Accuracy)) %>%
  dplyr::filter(catch_acc < 0.75) %>%
  mutate(subj_block = paste0(as.character(Subject), as.character(Block)))

# summarize ACCs by subject and system
sloutsky_acc_long <- sloutsky %>%
  mutate(subj_block = paste0(as.character(Subject), as.character(Block))) %>%
  dplyr::filter(subj_block %!in% poor_blocks$subj_block) %>%
  group_by(Subject, Block) %>%
  summarise(m_acc = mean(Accuracy))

# plot relationship between systems
sloutsky_acc_wide <- spread(sloutsky_acc_long, Block, m_acc)
ggplot(sloutsky_acc_wide, aes(SupervisedSparse, UnsupervisedDense)) + geom_point() + theme_bw() + geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Sloutsky Conditions - Accuracy")

# test correlation
cor.test(sloutsky_acc_wide$SupervisedSparse, sloutsky_acc_wide$UnsupervisedDense)

# violin plot of systems
sloutsky_acc_plot <- summarySE(sloutsky_acc_long, "m_acc", "Block")
ggplot(sloutsky_acc_long, aes(Block, m_acc)) + geom_violin() + 
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = sloutsky_acc_plot) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = sloutsky_acc_plot) +
  theme_bw() + xlab("Condition") + ylab("Accuracy") + ggtitle("Sloutsky Performance")
```

Create *z*-scores for accuracy.

```{r}
# select only relevant blocks, create new df
slout_acc_stand <- sloutsky_acc_long %>%
  dplyr::filter(Block == "SupervisedSparse" | Block == "UnsupervisedDense") %>%
  dplyr::select(Subject, Block, m_acc)
# z-scores
slout_acc_stand$acc_z <- scale(slout_acc_stand$m_acc)
# create column for system
slout_acc_stand$System <- NA
slout_acc_stand$System[slout_acc_stand$Block == "UnsupervisedDense"] <- "associative"
slout_acc_stand$System[slout_acc_stand$Block == "SupervisedSparse"] <- "hypothesis-testing"
# create column for paradigm
slout_acc_stand$CatLearn <- "sloutsky"
# df with raw acc
slout_acc <- slout_acc_stand[,-c(2,4)]
# df with acc z-scores
slout_acc_stand <- slout_acc_stand[,-c(2,3)]
```

## RT

```{r}
# recode non-answers to missing
sloutsky$RT[sloutsky$RT == 9999] <- NA

# same RT processing as above
sl_rt <- sloutsky %>%
  mutate(subj_block = paste0(as.character(Subject), as.character(Block))) %>%
  dplyr::filter(subj_block %!in% poor_blocks$subj_block) %>%
  dplyr::filter(Accuracy == 1) %>%
  group_by(Subject, Block) %>%
  mutate(mean_rt = mean(RT),
         sd_rt = sd(RT),
         diff = RT-mean_rt,
         remove = ifelse(abs(diff) > 2*sd_rt, 1, 0)) %>%
  dplyr::filter(remove == 0) %>%
  summarise(m_rt = mean(RT))

# plot by system
sl_plot_rt <- summarySE(sl_rt, "m_rt", "Block", na.rm = TRUE)
ggplot(sl_rt, aes(Block, m_rt)) + geom_violin() + 
  geom_point(aes(y = m_rt), size = 2, position = position_dodge((width = 0.90)), data = sl_plot_rt) +
  geom_errorbar(aes(ymin = m_rt-se, ymax = m_rt+se), width = 0.20, position = position_dodge((width = 0.90)), data = sl_plot_rt) +
  theme_bw() + xlab("Block") + ylab("RT") + ggtitle("Sloutsky Performance")

# plot to look for outliers
sl_rt %>%
  group_by(Block) %>%
  mutate(outlier = ifelse(is_outlier(m_rt), Subject, as.numeric(NA))) %>%
  ggplot(., aes(Block, m_rt)) + geom_boxplot() + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3) + theme_bw()
```

Here the RTs make sense -- Supervised (hypothesis-testing) is faster than unsupervised (associative), and match (SS and UD) are faster than mismatch (SD and US).

No single subject is an outlier across all conditions, so I won't be removing anyone.


```{r}
# select relevant blocks and plot relationship between the two
sl_filt <- dplyr::filter(sl_rt, Block %in% c("UnsupervisedDense","SupervisedSparse"))
sl_wide <- spread(sl_filt, Block, m_rt)
ggplot(sl_wide, aes(UnsupervisedDense, SupervisedSparse)) + geom_point() + theme_bw() + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Relationship Between Sloutsky Conditions - RT")
```

Standardizing Sloutsky RTs.

```{r}
# select new df
slout_rt_stand <- sl_filt
# z-scores
slout_rt_stand$rt_z <- scale(slout_rt_stand$m_rt)
# column for system
slout_rt_stand$System <- NA
slout_rt_stand$System[slout_rt_stand$Block == "UnsupervisedDense"] <- "associative"
slout_rt_stand$System[slout_rt_stand$Block == "SupervisedSparse"] <- "hypothesis-testing"
# column for paradigm
slout_rt_stand$CatLearn <- "sloutsky"
# df for raw RT
slout_rt <- slout_rt_stand[,-c(2,4)]
# df for RT z-scores
slout_rt_stand <- slout_rt_stand[,-c(2,3)]
```

# Processing/Standardizing Tax/Them Data

## Accuracy

```{r}
# select only the test trials
test_trials <- dplyr::filter(taxthem, !is.na(expTrials.thisTrialN))

# calculate mean acc by participant and system
tt_acc <- test_trials %>%
  group_by(participant, Experiment) %>%
  summarise(m_acc = mean(resp.corr))

# plot relationship between two systems
tt_acc_wide <- tt_acc %>%
  group_by(participant) %>%
  spread(key = Experiment, value = m_acc) 
ggplot(tt_acc_wide, aes(taxonomic, thematic)) + geom_point() + geom_smooth(se = FALSE, method = "lm") + theme_bw()

# test correlation
cor.test(tt_acc_wide$taxonomic, tt_acc_wide$thematic)  

# violin plot of both systems
tt_plot_acc <- summarySE(tt_acc, "m_acc", "Experiment")
ggplot(tt_acc, aes(Experiment, m_acc)) + geom_violin() + 
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = tt_plot_acc) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = tt_plot_acc) +
  theme_bw() + xlab("Condition") + ylab("Accuracy") + ggtitle("Tax/Them Performance")
```

Create *z*-scores for accuracy.

```{r}
# new df
tt_acc_stand <- tt_acc
# rename column
colnames(tt_acc_stand)[1] <- "Subject"
# z-score
tt_acc_stand$acc_z <- scale(tt_acc_stand$m_acc)
# column for system
tt_acc_stand$System <- NA
tt_acc_stand$System[tt_acc_stand$Experiment == "taxonomic"] <- "hypothesis-testing"
tt_acc_stand$System[tt_acc_stand$Experiment == "thematic"] <- "associative"
# column for paradigm
tt_acc_stand$CatLearn <- "tt"
# df for raw acc
tt_acc <- tt_acc_stand[,-c(2,4)]
# df for acc z-score
tt_acc_stand <- tt_acc_stand[,-c(2,3)]
```

## RT

```{r}
# same RT processing as above
tt_rt <- test_trials %>%
  dplyr::filter(resp.corr == 1) %>%
  group_by(participant, Experiment) %>%
  mutate(mean_rt = mean(resp.rt),
         sd_rt = sd(resp.rt),
         diff = resp.rt-mean_rt,
         remove = ifelse(abs(diff) > 2*sd_rt, 1, 0)) %>%
  dplyr::filter(remove == 0) %>%
  summarise(m_rt = mean(resp.rt))

# violin plots by system
tt_plot_rt <- summarySE(tt_rt, "m_rt", "Experiment")
ggplot(tt_rt, aes(Experiment, m_rt)) + geom_violin() + 
  geom_point(aes(y = m_rt), size = 2, position = position_dodge((width = 0.90)), data = tt_plot_rt) +
  geom_errorbar(aes(ymin = m_rt-se, ymax = m_rt+se), width = 0.20, position = position_dodge((width = 0.90)), data = tt_plot_rt) +
  theme_bw() + xlab("Condition") + ylab("RT") + ggtitle("Tax/Them Performance")

# outlier plot
tt_rt %>%
  group_by(Experiment) %>%
  mutate(outlier = ifelse(is_outlier(m_rt), participant, as.numeric(NA))) %>%
  ggplot(., aes(Experiment, m_rt)) + geom_boxplot() + geom_text(aes(label = outlier), na.rm = TRUE, hjust = -0.3) + theme_bw()

# 8147 and 8048 are clear outliers in both conditions, so I will remove them.
tt_rt <- dplyr::filter(tt_rt, participant != 8147, participant != 8048)

# violin plot by system
tt_plot_rt <- summarySE(tt_rt, "m_rt", "Experiment")
ggplot(tt_rt, aes(Experiment, m_rt)) + geom_violin() + 
  geom_point(aes(y = m_rt), size = 2, position = position_dodge((width = 0.90)), data = tt_plot_rt) +
  geom_errorbar(aes(ymin = m_rt-se, ymax = m_rt+se), width = 0.20, position = position_dodge((width = 0.90)), data = tt_plot_rt) +
  theme_bw() + xlab("Condition") + ylab("RT") + ggtitle("Tax/Them Performance")
```

Create *z*-scores for RT

```{r}
# new df
tt_rt_stand <- tt_rt
# rename column
colnames(tt_rt_stand)[1] <- "Subject"
# z-score
tt_rt_stand$rt_z <- scale(tt_rt_stand$m_rt)
# column for system
tt_rt_stand$System <- NA
tt_rt_stand$System[tt_rt_stand$Experiment == "taxonomic"] <- "hypothesis-testing"
tt_rt_stand$System[tt_rt_stand$Experiment == "thematic"] <- "associative"
# column for paradigm
tt_rt_stand$CatLearn <- "tt"
# df for raw rts
tt_rt <- tt_rt_stand[,-c(2,4)]
# df for rt z-scores
tt_rt_stand <- tt_rt_stand[,-c(2,3)]
```

# Combining the 3 experiments

## Accuracy

```{r}
# merge the data frames together
acc_long <- dplyr::bind_rows(ashby_acc_stand, slout_acc_stand, tt_acc_stand)
acc_wide <- acc_long %>%
  spread(key = CatLearn, value = acc_z) %>%
  na.omit

# find which subjects have full data for both systems and only use those subjects
both_systems <- acc_wide$Subject[duplicated(acc_wide$Subject)]
acc_wide <- dplyr::filter(acc_wide, Subject %in% both_systems)

# test the normality of the different variables
dagoTest(acc_wide$ashby)
dagoTest(acc_wide$sloutsky)
dagoTest(acc_wide$tt)

# sloutsky and tt are skewed, so let's transform. ashby is almost skewed, why not.
vars_tf <- c("ashby","sloutsky", "tt")
# transformations
pp_md_tf <- caret::preProcess(as.data.frame(acc_wide[,vars_tf]), method = c("center", "scale", "YeoJohnson"), na.remove=T)
tf_data <- predict(pp_md_tf, as.data.frame(acc_wide[,vars_tf]))
# re-check normality
dagoTest(tf_data$ashby)
dagoTest(tf_data$sloutsky)
dagoTest(tf_data$tt)
# less skewed at least

# move data into main data frame
acc_wide$ashby.t <- tf_data$ashby
acc_wide$sloutsky.t <- tf_data$sloutsky
acc_wide$tt.t <- tf_data$tt

write.csv(acc_wide, "catlearn_proc_acc.csv")

# merge in age and gender
acc_demo <- acc_wide %>%
  inner_join(.,age_gender, by = "Subject")

# only select first 84 subjects (per preregistration)
acc_sel <- acc_demo[c(1:(2*84)),]


acc_sel$Gender[acc_sel$Gender == "female"] <- "Female"
acc_sel$Gender[acc_sel$Gender == "male"] <- "Male"
# demographics for this sample
acc_sel %>%
  distinct(Subject, Age, Gender) %>%
  group_by(Gender) %>%
  dplyr::count(Gender)

acc_sel %>%
  distinct(Subject, Age, Gender) %>%
  ungroup() %>%
  summarise(m_age = mean(Age),
            sd_age = sd(Age),
            min_age = min(Age),
            max_age = max(Age))

# select only the hypothesis testing data and see their correlation
ht <- subset(acc_sel, System == "hypothesis-testing")
cor.mat <- cor(ht[,c(6:8)])
p.mat <- cor_pmat(ht[,c(6:8)])
ggcorrplot(cor.mat, type = "lower", p.mat = p.mat, lab = TRUE, title = "ACC - Hypothesis-testing")

# same with associative
as <- subset(acc_sel, System == "associative")
cor(as[,c(6:8)])
cor.mat <- cor(as[,c(6:8)])
p.mat <- cor_pmat(as[,c(6:8)])
ggcorrplot(cor.mat, type = "lower", p.mat = p.mat, lab = TRUE, title = "ACC - Associative")

# Plot accuracy
acc_sel_long <- acc_sel %>%
  dplyr::select(Subject, System, ashby.t:tt.t) %>%
  gather(key ="CatLearn", value = "acc_z", ashby.t:tt.t)

acc_sel_long <- acc_sel_long %>%
  mutate(CatLearn = revalue(CatLearn, c("ashby.t" = "Perceptual\ncategory", "sloutsky.t" = "Statistical\ndensity", "tt.t" = "Taxonomic-\nthematic")),
         System = revalue(System, c("associative" = "Associative", "hypothesis-testing" = "Hypothesis-testing")))


# by system
acc_all_plot <- summarySE(acc_sel_long, "acc_z", c("System", "CatLearn"))
ggplot(acc_sel_long, aes(CatLearn, acc_z)) + geom_violin() + 
  geom_point(aes(y = acc_z), size = 2, position = position_dodge((width = 0.90)), data = acc_all_plot) +
  geom_errorbar(aes(ymin = acc_z-se, ymax = acc_z+se), width = 0.20, position = position_dodge((width = 0.90)), data = acc_all_plot) +
  facet_grid(.~System) +
  theme_bw() + xlab("Experiment") + ylab("Accuracy Z-Score (transformed)") + ggtitle("")

# by paradigm
ggplot(acc_sel_long, aes(System, acc_z)) + geom_violin() + 
  geom_point(aes(y = acc_z), size = 2, position = position_dodge((width = 0.90)), data = acc_all_plot) +
  geom_errorbar(aes(ymin = acc_z-se, ymax = acc_z+se), width = 0.20, position = position_dodge((width = 0.90)), data = acc_all_plot) +
  facet_grid(.~CatLearn) +
  theme_bw(15) + xlab("Experiment") + ylab("Accuracy Z-Score (transformed)") + ggtitle("")

# run basic models
m0 <- lmer(acc_z ~ 1 + (1|Subject), data = acc_sel_long)
ranova(m0)
m1 <- lmer(acc_z ~ CatLearn + System + (1|Subject), data = acc_sel_long)
anova(m0,m1)
m2 <- lmer(acc_z ~ CatLearn * System + (1|Subject), data = acc_sel_long)
anova(m1,m2)
summary(m2)
anova(m2)

# break down interaction between paradigm and system
ashby_subset <- acc_sel_long$CatLearn=="Perceptual\ncategory"
sloutsky_subset <- acc_sel_long$CatLearn=="Statistical\ndensity"
tt_subset <- acc_sel_long$CatLearn=="Taxonomic-\nthematic"

# check ashby first
ashby_model <- lmer(acc_z ~ System + (1|Subject), data = acc_sel_long, subset = ashby_subset)
summary(ashby_model)
anova(ashby_model)
# look at post hocs
summary(glht(ashby_model, linfct = mcp(System = "Tukey")), test = adjusted("holm"))

# sloutsky 
sloutsky_model <- lmer(acc_z ~ System + (1|Subject), data = acc_sel_long, subset = sloutsky_subset)
summary(sloutsky_model)
anova(sloutsky_model)
# look at post hocs
summary(glht(sloutsky_model, linfct = mcp(System = "Tukey")), test = adjusted("holm"))

# tt 
tt_model <- lmer(acc_z ~ System + (1|Subject), data = acc_sel_long, subset = tt_subset)
summary(tt_model)
anova(tt_model)
# look at post hocs
summary(glht(tt_model, linfct = mcp(System = "Tukey")), test = adjusted("holm"))
```



## RT

```{r}
# bring together RT data
rt_long <- dplyr::bind_rows(ashby_rt_stand, slout_rt_stand, tt_rt_stand)

# make a wide dataset
rt_wide <- rt_long %>%
  spread(key = CatLearn, value = rt_z) %>%
  na.omit

# find which subjects have both systems and keep those
both_systems <- rt_wide$Subject[duplicated(rt_wide$Subject)]
rt_wide <- dplyr::filter(rt_wide, Subject %in% both_systems)

# check normality
dagoTest(rt_wide$ashby)
dagoTest(rt_wide$sloutsky)
dagoTest(rt_wide$tt)

# all are very skewed. transform.
vars_tf <- c("ashby", "sloutsky", "tt")
pp_md_tf <- preProcess(as.data.frame(rt_wide[,vars_tf]), method = c("center", "scale", "YeoJohnson"), na.remove=T)
tf_data <- predict(pp_md_tf, as.data.frame(rt_wide[,vars_tf]))

# re-check normality
dagoTest(tf_data$ashby)
dagoTest(tf_data$sloutsky)
dagoTest(tf_data$tt)
# way better!

# add to main dataframe
rt_wide$ashby.t <- tf_data$ashby
rt_wide$sloutsky.t <- tf_data$sloutsky
rt_wide$tt.t <- tf_data$tt

write.csv(rt_wide, "catlearn_proc_rt.csv")

# select only first 84 subjects (per preregistration)
rt_sel <- rt_wide[c(1:(2*84)),]

# look at correlations
# first for hypothesis-testing
ht <- subset(rt_sel, System == "hypothesis-testing")
cor.mat <- cor(ht[,c(6:8)])
p.mat <- cor_pmat(ht[,c(6:8)])
ggcorrplot(cor.mat, type = "lower", p.mat = p.mat, lab = TRUE, title = "RTs - Hypothesis-testing")

# now hypothesis testing
as <- subset(rt_sel, System == "associative")
cor.mat <- cor(as[,c(6:8)])
p.mat <- cor_pmat(as[,c(6:8)])
ggcorrplot(cor.mat, type = "lower", p.mat = p.mat, lab = TRUE, title = "RTs - Associative")

rt_sel_long <- rt_sel %>%
  dplyr::select(Subject, System, ashby.t:tt.t) %>%
  gather(key ="CatLearn", value = "rt_z", ashby.t:tt.t)

rt_sel_long <- rt_sel_long %>%
  mutate(CatLearn = revalue(CatLearn, c("ashby.t" = "Perceptual\ncategory", "sloutsky.t" = "Statistical\ndensity", "tt.t" = "Taxonomic-\nthematic")),
         System = revalue(System, c("associative" = "Associative", "hypothesis-testing" = "Hypothesis-testing")))

# now plot
# first by system
rt_all_plot <- summarySE(rt_sel_long, "rt_z", c("System", "CatLearn"))
ggplot(rt_sel_long, aes(CatLearn, rt_z)) + geom_violin() + 
  geom_point(aes(y = rt_z), size = 2, position = position_dodge((width = 0.90)), data = rt_all_plot) +
  geom_errorbar(aes(ymin = rt_z-se, ymax = rt_z+se), width = 0.20, position = position_dodge((width = 0.90)), data = rt_all_plot) +
  facet_grid(.~System) +
  theme_bw(15) + xlab("Experiment") + ylab("RT z-Score") + ggtitle("")

# then by paradigm
ggplot(rt_sel_long, aes(System, rt_z)) + geom_violin() + 
  geom_point(aes(y = rt_z), size = 2, position = position_dodge((width = 0.90)), data = rt_all_plot) +
  geom_errorbar(aes(ymin = rt_z-se, ymax = rt_z+se), width = 0.20, position = position_dodge((width = 0.90)), data = rt_all_plot) +
  facet_grid(.~CatLearn) +
  theme_bw() + xlab("Experiment") + ylab("RT Z-Score (transformed)") + ggtitle("")

m0 <- lmer(rt_z ~ 1 + (1|Subject), data = rt_sel_long)
ranova(m0)
m1 <- lmer(rt_z ~ CatLearn + System + (1|Subject), data = rt_sel_long)
anova(m0,m1)
m2 <- lmer(rt_z ~ CatLearn * System + (1|Subject), data = rt_sel_long)
anova(m1,m2)
summary(m2)
anova(m2)

summary(glht(m1, linfct = mcp(System = "Tukey")), test = adjusted("holm"))
```

We only see a main effect of system -- where associative is consistently slower than hypothesis-testing.

## Descriptives

```{r}
# bind together raw ACC and RT dfs
acc <- dplyr::bind_rows(ashby_acc, slout_acc, tt_acc)
rt <- dplyr::bind_rows(ashby_rt, slout_rt, tt_rt)



# make them into wide dfs, omit missing cells
acc_wide <- acc %>%
  spread(key = CatLearn, value = m_acc) %>%
  na.omit

both_systems <- acc_wide$Subject[duplicated(acc_wide$Subject)]
acc_wide <- dplyr::filter(acc_wide, Subject %in% both_systems)

rt_wide <- rt %>%
  spread(key = CatLearn, value = m_rt) %>%
  na.omit

both_systems <- rt_wide$Subject[duplicated(rt_wide$Subject)]
rt_wide <- dplyr::filter(rt_wide, Subject %in% both_systems)

# make them long again, select only first 24 subjects
acc_group <- acc_wide[c(1:(2*84)),] %>%
  gather(key = "CatLearn", value = "m_acc", ashby:tt)
rt_group <- rt_wide[c(1:(2*84)),] %>%
  gather(key = "CatLearn", value = "m_rt", ashby:tt)

# merge together
data <- merge(acc_group, rt_group, by = c("Subject", "CatLearn", "System"))

# print out summary statistics
data %>%
  gather(key = "measure", value = "value", m_acc:m_rt) %>%
  group_by(CatLearn, measure, System) %>%
  summarise(m = mean(value),
            SD = sd(value), 
            min = min(value),
            max = max(value))

# look at ceiling effects
acc_group %>%
  dplyr::filter(m_acc >= 0.9) %>%
  group_by(System, CatLearn) %>%
  summarise(count = n())

acc_all_plot <- summarySE(acc_group, "m_acc", c("System", "CatLearn"))
acc_group %>%
  ggplot(.,aes(System, m_acc)) + geom_violin() +
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = acc_all_plot) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = acc_all_plot) +
  facet_grid(.~CatLearn) +
  theme_bw(15) + xlab("Experiment") + ylab("Accuracy") + ggtitle("")


rt_group_nott <-subset(rt_group, CatLearn !="tt")
rt_all_plot <- summarySE(rt_group, "m_rt", c("System", "CatLearn"))
rt_group %>%
  ggplot(.,aes(System, m_rt)) + geom_violin() +
  geom_point(aes(y = m_rt), size = 2, position = position_dodge((width = 0.90)), data = rt_all_plot) +
  geom_errorbar(aes(ymin = m_rt-se, ymax = m_rt+se), width = 0.20, position = position_dodge((width = 0.90)), data = rt_all_plot) +
  facet_grid(.~CatLearn) +
  theme_bw(15) + xlab("Experiment") + ylab("RT") + ggtitle("")
  
```


# Learning Over Time

## Ashby

```{r}
se <- function(x) sqrt(var(x)/length(x))

ashby_full %>%
  mutate(Block = as.factor(Block)) %>%
  group_by(Type, Block, Overall_Trial) %>%
  summarise(m_acc = mean(Accuracy),
            se_acc = se(Accuracy)) %>%
  ggplot(.,aes(Overall_Trial, m_acc, color = Block)) + geom_point() + facet_grid(.~Type) +
  geom_errorbar(aes(ymin = m_acc-se_acc, ymax = m_acc+se_acc), width = 0.20, position = position_dodge((width = 0.90))) +
  theme_bw() + geom_line() + xlab("Overall Trial") + ylab("Mean Accuracy (across subjects)") + ggtitle("Ashby Task Accuracy over Time")

ashby_full %>%
  mutate(Block = as.factor(Block)) %>%
  dplyr::filter(Accuracy == 1) %>% # selecting correct trials only
  group_by(Subject, Type) %>%
  mutate(mean_rt = mean(RT),
         sd_rt = sd(RT),
         diff = RT-mean_rt,
         remove = ifelse(abs(diff) > 2*sd_rt, 1, 0)) %>% # if any trial has an RT more than 2SD away from the mean, flag it for removal
  dplyr::filter(remove == 0, Trial > 1) %>%
  group_by(Type, Block, Overall_Trial) %>%
  summarise(m_acc = mean(Accuracy),
            se_acc = se(Accuracy),
            m_rt = mean(RT),
            se_rt = se(RT)) %>%
  ggplot(.,aes(Overall_Trial, m_rt, color = Block)) + geom_point() + facet_grid(.~Type) +
  geom_errorbar(aes(ymin = m_rt-se_rt, ymax = m_rt+se_rt), width = 0.20, position = position_dodge((width = 0.90))) +
  theme_bw() + geom_line()+ xlab("Overall Trial") + ylab("Mean RT (across subjects)") + ggtitle("Ashby Task RT over Time")

```


## Sloutsky

```{r}
sloutsky %>%
  mutate(subj_block = paste0(as.character(Subject), as.character(Block))) %>%
  dplyr::filter(subj_block %!in% poor_blocks$subj_block) %>%
  group_by(Block, Trial) %>%
  summarise(m_acc = mean(Accuracy),
            se_acc = se(Accuracy)) %>%
  ggplot(.,aes(Trial, m_acc, color = Block)) + geom_point()  +
  geom_errorbar(aes(ymin = m_acc-se_acc, ymax = m_acc+se_acc), width = 0.20) +
  theme_bw() + geom_line() + xlab("Overall Trial") + ylab("Mean Accuracy (across subjects)") + ggtitle("Sloutsky Task Accuracy over Time")

sloutsky_rt <- sloutsky %>%
  mutate(subj_block = paste0(as.character(Subject), as.character(Block))) %>%
  dplyr::filter(subj_block %!in% poor_blocks$subj_block) %>%
  dplyr::filter(Accuracy == 1) %>% # selecting correct trials only
  group_by(Subject, Block) %>%
  mutate(mean_rt = mean(RT),
         sd_rt = sd(RT),
         diff = RT-mean_rt,
         remove = ifelse(abs(diff) > 2*sd_rt, 1, 0)) %>% # if any trial has an RT more than 2SD away from the mean, flag it for removal
  dplyr::filter(remove == 0) %>%
  group_by(Block, Trial) %>%
  summarise(m_rt = mean(RT),
            se_rt = se(RT)) %>%
  ggplot(.,aes(Trial, m_rt, color = Block)) + geom_point() +
  geom_errorbar(aes(ymin = m_rt-se_rt, ymax = m_rt+se_rt), width = 0.20) +
  theme_bw() + geom_line() + xlab("Overall Trial") + ylab("Mean RT (across subjects)") + ggtitle("Sloutsky Task RT over Time") 

t <- poly((unique(sloutsky_rt$Trial)), 3)
sloutsky_rt[,paste("ot", 1:3, sep="")] <- t[sloutsky_rt$Trial, 1:3]

m1 <- lmer(RT ~ (ot1+ot2+ot3)*(Block) +
                                (ot1+ot2+ot3 | Subject) +
                                (ot1+ot2 | Block:Subject),
                      control = lmerControl(optimizer = "bobyqa"), 
                      data = sloutsky_rt, REML = F)
sloutsky_rt$fitted <- fitted(m1)



p_GCA <-
ggplot(sloutsky_rt, aes(Trial, RT, shape = Block)) +
  stat_summary(aes(y = fitted, linetype = Block, color = Block), fun.y = mean, geom = "line") +
  #stat_summary(fun.y = mean, geom = "point", size = 4, fill = "white", aes(color = Block)) +
  #scale_shape_manual(values = c(1,2,3,4)) +
  scale_linetype_manual(values = c("solid", "longdash", "dotted","twodash")) +
  scale_fill_manual(values = c("blue", "red", "black", "green")) +
  scale_color_manual(values = c("blue", "red", "black", "green")) +
  theme_bw()

ggplot(sloutsky_rt, aes(Trial, ot1)) + geom_point()
ggplot(sloutsky_rt, aes(Trial, ot2)) + geom_point()
ggplot(sloutsky_rt, aes(Trial, ot3)) + geom_point()
```


# First-block only for sloutsky

```{r}
first_block_sl <- sloutsky %>%
  mutate(subj_block = paste0(as.character(Subject), as.character(Block))) %>%
  dplyr::filter(subj_block %!in% poor_blocks$subj_block) %>%
  group_by(Subject) %>%
  dplyr::filter(BlockNum == 1) %>%
  group_by(Subject,Block) %>%
  summarise(m_acc = mean(Accuracy))
  
sl_plot <- summarySE(first_block_sl, "m_acc", "Block", na.rm =TRUE)
ggplot(first_block_sl, aes(Block, m_acc)) + geom_violin() + 
  geom_point(aes(y = m_acc), size = 2, position = position_dodge((width = 0.90)), data = sl_plot) +
  geom_errorbar(aes(ymin = m_acc-se, ymax = m_acc+se), width = 0.20, position = position_dodge((width = 0.90)), data = sl_plot) +
  theme_bw() + xlab("Condition") + ylab("Accuracy (raw)") + ggtitle("") + ylim(0,1)


first_block_sl <- sloutsky %>%
  mutate(subj_block = paste0(as.character(Subject), as.character(Block))) %>%
  dplyr::filter(subj_block %!in% poor_blocks$subj_block) %>%
  group_by(Subject) %>%
  dplyr::filter(BlockNum == 1) %>%
  group_by(Subject,Block) %>%
  mutate(acc_type = ifelse(StimType == "target" & RESP == "target", "hit", ifelse(StimType == "nottarget" & RESP =="target", "fa", NA))) %>%
  group_by(Subject, Block, acc_type) %>%
  summarise(count = n()) %>%
  na.omit() %>%
  spread(key = acc_type, value = count) %>%
  mutate(fa = replace_na(fa, 0),
         fa_pct = fa/16,
         hit_pct = hit/16,
         hit_fa_pct = hit_pct - fa_pct)

sl_plot <- summarySE(first_block_sl, "hit_fa_pct", "Block", na.rm =TRUE)
ggplot(first_block_sl, aes(Block, hit_fa_pct)) + geom_violin() + 
  geom_point(aes(y = hit_fa_pct), size = 2, position = position_dodge((width = 0.90)), data = sl_plot) +
  geom_errorbar(aes(ymin = hit_fa_pct-se, ymax = hit_fa_pct+se), width = 0.20, position = position_dodge((width = 0.90)), data = sl_plot) +
  theme_bw() + xlab("Condition") + ylab("Accuracy (Hit - FA)") + ggtitle("") + ylim(0,1)

```



